AP/PA Tables ITHIM Global

### 2023-08-14 summary_tables.Rmd

  # city <- "antofagasta"

  td <- io[[city]]$outcomes$mmets %>% dplyr::select(ends_with("mmet")) %>%
    rename("Baseline" = base_mmet, "CYC_SC" = sc_cycle_mmet,
           "CAR_SC" = sc_car_mmet,  "BUS_SC" = sc_bus_mmet,
           "MOT_SC" = sc_motorcycle_mmet) %>% 
    summarise(across(, ~ quantile(.x, c(0.05,0.10,0.25, 0.375, 0.50,0.75,0.90), na.rm = T)), 
              prob = c(0.05,0.10,0.25, 0.375, 0.50,0.75,0.90)) %>%
    pivot_longer(cols = -c(prob)) %>% mutate(city = city)

  td1 <- io[[city]]$outcomes$mmets %>% dplyr::select(ends_with("mmet")) %>%
     rename("Baseline" = base_mmet, "CYC_SC" = sc_cycle_mmet,
           "CAR_SC" = sc_car_mmet,  "BUS_SC" = sc_bus_mmet,
           "MOT_SC" = sc_motorcycle_mmet) %>% 
    summarise(across(, ~ mean(.x))) %>%  t() %>% as.data.frame() %>% 
    tibble::rownames_to_column("name") %>% 
    rename(value = V1) %>% 
    mutate(prob = "mean") %>% mutate(city = city)

>>>>

  td <- io[[city]]$outcomes$mmets %>% dplyr::select(ends_with("mmet")) |> 
    rename_with(recode, base_mmet = "Baseline", sc_cycle_mmet = "CYC_SC",
           sc_car_mmet = "CAR_SC",  sc_bus_mmet = "BUS_SC",
           sc_motorcycle_mmet = "MOT_SC") %>% 
    summarise(across(, ~ quantile(.x, c(0.05,0.10,0.25, 0.375, 0.50,0.75,0.90), na.rm = T)), 
              prob = c(0.05,0.10,0.25, 0.375, 0.50,0.75,0.90)) %>%
    pivot_longer(cols = -c(prob)) %>% mutate(city = city)

  td1 <- io[[city]]$outcomes$mmets %>% dplyr::select(ends_with("mmet")) %>%
     rename_with(recode, base_mmet = "Baseline", sc_cycle_mmet = "CYC_SC",
           sc_car_mmet = "CAR_SC",  sc_bus_mmet = "BUS_SC",
           sc_motorcycle_mmet = "MOT_SC") |> 
    summarise(across(, ~ mean(.x))) %>%  t() %>% as.data.frame() %>% 
    tibble::rownames_to_column("name") %>% 
    rename(value = V1) %>% 
    mutate(prob = "mean") %>% mutate(city = city)

### 2023-08-14 summary_tables_PA_AP.Rmd

input_parameter_file <- "InputParameters_v28.0.xlsx"
# scenario definition
scenario_name <- "GLOBAL"
reference_scenario <- 'Baseline'

@@

  n_col <- ncol(io[[cities[x]]]$outcomes$pm_conc_pp)
  names(io[[cities[x]]]$outcomes$pm_conc_pp)[(n_col - 4):n_col] <- scen_names

  data_long <- gather(io[[cities[x]]]$outcomes$pm_conc_pp, scenario, pm_conc,
                      Baseline:`Motorcycling`, factor_key = TRUE)
  y <- ggplot(data_long, aes(x = scenario, y = pm_conc, fill = scenario)) +
    geom_boxplot(outlier.shape = 8) + ggtitle(cities[x]) +
    labs(y = "Daily PM2.5 Concentration", x = "Scenarios") #+
  # +ylim(low[x],high[x])
  # yy <- ggplot() +
  #   geom_density(data_long, aes(x = scenario, y = pm_conc, fill = scenario)) +
  #   ggtitle(cities[x]) +
  #   labs(y = "Daily PM2.5 Concentration", x = "Scenarios")
  print(y)
  #print(yy)
  # l[[i]] <- ggplotly(ggplot(data_long, aes(x = scenario, y = pm_conc, fill = scenario)) +
  #   geom_boxplot(outlier.shape = 8) + ggtitle(cities[x]) +
  #   labs(y = "Daily PM2.5 Concentration", x = "Scenarios"))
  # print(ggplotly(yy))
}
```

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
data_long <- NA
summary <- NA
for (x in 1:length(cities)) {
  #names(io[[cities[x]]]$outcomes$pm_conc_pp)[6:11]<-c("Baseline","Walking", "Bicycling", "Driving", "Motorcycling", "Public Transport")
  #
  n_col <- ncol(io[[cities[x]]]$outcomes$pm_conc_pp)
  names(io[[cities[x]]]$outcomes$pm_conc_pp)[(n_col - 4):n_col] <- scen_names
  data_long <- gather(io[[cities[x]]]$outcomes$pm_conc_pp, scenario, pm_conc,
                      Baseline:`Motorcycling`, factor_key = TRUE)
  summary <- as.data.frame(data_long %>% group_by(scenario) %>%
                             summarise('mean' = mean(pm_conc),
                                       '5th' = quantile(pm_conc, 0.05),
                                       '50th' = quantile(pm_conc, 0.5),
                                       '95th' = quantile(pm_conc, 0.9)))
  summary <- cbind(summary$scenario ,round(summary[,2:5], digits = 1))
  summary$scenario_PM <- round(io[[cities[x]]]$outcomes$scenario_pm, digits=2)
  summary$change_PM <- round(io[[cities[x]]]$outcomes$scenario_pm - io[[cities[x]]]$outcomes$scenario_pm[1], digits=2)
  names(summary)[1] <- "Scenario"
  print(kable(summary, caption = cities[x]))

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
limit = 100
for (x in 1:length(cities)) {
  n_col <- ncol(io[[cities[x]]]$outcomes$mmets)
  names(io[[cities[x]]]$outcomes$mmets)[(n_col - 4):n_col] <- scen_names

  data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, Baseline:`Motorcycling`, factor_key = TRUE)
  y <- ggplot(data_long, aes(x = scenario, y = mmet, fill = scenario)) +
    geom_boxplot(outlier.shape = NA) + ggtitle(cities[x]) + 
    labs(y = "Weekly MMET", x = "Scenarios")+  ylim(0, limit)
  print(y)

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
for (x in 1:length(cities)) {
  #names(io[[cities[x]]]$outcomes$mmets)[5:10] <- c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen")
  n_col <- ncol(io[[cities[x]]]$outcomes$mmets)
  names(io[[cities[x]]]$outcomes$mmets)[(n_col - 4):n_col] <- scen_names

  data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, Baseline:Motorcycling, factor_key = TRUE)
  summary <- as.data.frame(data_long %>% group_by(scenario) %>% 
                             summarise('mean' = mean(mmet),
                                       '5th' = quantile(mmet, 0.05),
                                       '50th' = quantile(mmet, 0.5),
                                       '95th' = quantile(mmet, 0.9)))
  summary <- cbind(summary$scenario ,round(summary[,2:5], digits = 1))
  names(summary)[1] <- "Scenario"
  print(kable(summary, caption = cities[x]))

@@

  td <- round(colMeans(io[[city]]$outcomes$mmets[,(n_col - 4):n_col], na.rm = T), 1) %>%
    as.data.frame() %>% tibble::rownames_to_column()
  names(td) <- c('Scenario', city)

@@

  names(io[[cities[x]]]$outcomes$pm_conc_pp)[(n_col - 4):n_col] <- scen_names

  data_long <- gather(io[[cities[x]]]$outcomes$pm_conc_pp, scenario, pm_conc,
                      Baseline:`Motorcycling`, factor_key = TRUE)

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
limit = 100
for (x in 1:length(cities)) {
  n_col <- ncol(io[[cities[x]]]$outcomes$mmets)
  names(io[[cities[x]]]$outcomes$mmets)[(n_col - 4):n_col] <- scen_names
  data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, Baseline:`Motorcycling`, factor_key = TRUE)
  y <- ggplot(data_long, aes(x = scenario, y = mmet, fill = scenario)) + geom_boxplot(outlier.shape = NA) + ggtitle(cities[x]) + 
    labs(y = "Weekly MMET", x = "Scenarios") + ylim(0, limit)
  print(y)

>>>>

NUMS <- io$scen_prop |> nrow()

if (NUMS != 4)
  scen_names <- c("Baseline", "Bicycling", "Driving", "Public Transport")

scen_length <- length(scen_names) - 1

if (!exists("input_parameter_file"))
  input_parameter_file <<- "InputParameters_v30.1.xlsx"
# scenario definition
scenario_name <- "GLOBAL"
reference_scenario <- 'Baseline'

@@

  n_col <- ncol(io[[cities[x]]]$outcomes$pm_conc_pp)
  names(io[[cities[x]]]$outcomes$pm_conc_pp)[(n_col - scen_length):n_col] <- scen_names

  data_long <- gather(io[[cities[x]]]$outcomes$pm_conc_pp, scenario, pm_conc,
                      Baseline:scen_names[length(scen_names)], factor_key = TRUE)
  y <- ggplot(data_long, aes(x = scenario, y = pm_conc, fill = scenario)) +
    geom_boxplot(outlier.shape = 8) + ggtitle(cities[x]) +
    labs(y = "Daily PM2.5 Concentration", x = "Scenarios") #+
  # +ylim(low[x],high[x])
  # yy <- ggplot() +
  #   geom_density(data_long, aes(x = scenario, y = pm_conc, fill = scenario)) +
  #   ggtitle(cities[x]) +
  #   labs(y = "Daily PM2.5 Concentration", x = "Scenarios")
  print(y)
  #print(yy)
  # l[[i]] <- ggplotly(ggplot(data_long, aes(x = scenario, y = pm_conc, fill = scenario)) +
  #   geom_boxplot(outlier.shape = 8) + ggtitle(cities[x]) +
  #   labs(y = "Daily PM2.5 Concentration", x = "Scenarios"))
  # print(ggplotly(yy))
}
```

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
data_long <- NA
summary <- NA
for (x in 1:length(cities)) {
  #names(io[[cities[x]]]$outcomes$pm_conc_pp)[6:11]<-c("Baseline","Walking", "Bicycling", "Driving", "Motorcycling", "Public Transport")
  #
  n_col <- ncol(io[[cities[x]]]$outcomes$pm_conc_pp)
  names(io[[cities[x]]]$outcomes$pm_conc_pp)[(n_col - scen_length):n_col] <- scen_names
  data_long <- gather(io[[cities[x]]]$outcomes$pm_conc_pp, scenario, pm_conc,
                      Baseline:scen_names[length(scen_names)], factor_key = TRUE)
  summary <- as.data.frame(data_long %>% group_by(scenario) %>%
                             summarise('mean' = mean(pm_conc),
                                       '5th' = quantile(pm_conc, 0.05),
                                       '50th' = quantile(pm_conc, 0.5),
                                       '95th' = quantile(pm_conc, 0.9)))
  summary <- cbind(summary$scenario ,round(summary[,2:5], digits = 1))
  summary$scenario_PM <- round(io[[cities[x]]]$outcomes$scenario_pm, digits=2)
  summary$change_PM <- round(io[[cities[x]]]$outcomes$scenario_pm - io[[cities[x]]]$outcomes$scenario_pm[1], digits=2)
  names(summary)[1] <- "Scenario"
  print(kable(summary, caption = cities[x]))

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
limit = 100
for (x in 1:length(cities)) {
  n_col <- ncol(io[[cities[x]]]$outcomes$mmets)
  names(io[[cities[x]]]$outcomes$mmets)[(n_col - scen_length):n_col] <- scen_names

  data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, Baseline:scen_names[length(scen_names)], factor_key = TRUE)
  y <- ggplot(data_long, aes(x = scenario, y = mmet, fill = scenario)) +
    geom_boxplot(outlier.shape = NA) + ggtitle(cities[x]) + 
    labs(y = "Weekly MMET", x = "Scenarios")+  ylim(0, limit)
  print(y)

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
for (x in 1:length(cities)) {
  #names(io[[cities[x]]]$outcomes$mmets)[5:10] <- c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen")
  n_col <- ncol(io[[cities[x]]]$outcomes$mmets)
  names(io[[cities[x]]]$outcomes$mmets)[(n_col - scen_length):n_col] <- scen_names

  data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, Baseline:scen_names[length(scen_names)], factor_key = TRUE)
  summary <- as.data.frame(data_long %>% group_by(scenario) %>% 
                             summarise('mean' = mean(mmet),
                                       '5th' = quantile(mmet, 0.05),
                                       '50th' = quantile(mmet, 0.5),
                                       '95th' = quantile(mmet, 0.9)))
  summary <- cbind(summary$scenario ,round(summary[,2:5], digits = 1))
  names(summary)[1] <- "Scenario"
  print(kable(summary, caption = cities[x]))

@@

  td <- round(colMeans(io[[city]]$outcomes$mmets[,(n_col - scen_length):n_col], na.rm = T), 1) %>%
    as.data.frame() %>% tibble::rownames_to_column()
  names(td) <- c('Scenario', city)

@@

  names(io[[cities[x]]]$outcomes$pm_conc_pp)[(n_col - scen_length):n_col] <- scen_names

  data_long <- gather(io[[cities[x]]]$outcomes$pm_conc_pp, scenario, pm_conc,
                      Baseline:scen_names[length(scen_names)], factor_key = TRUE)

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
limit = 100
for (x in 1:length(cities)) {
  n_col <- ncol(io[[cities[x]]]$outcomes$mmets)
  names(io[[cities[x]]]$outcomes$mmets)[(n_col - scen_length):n_col] <- scen_names
  data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, Baseline:scen_names[length(scen_names)], factor_key = TRUE)
  y <- ggplot(data_long, aes(x = scenario, y = mmet, fill = scenario)) + geom_boxplot(outlier.shape = NA) + ggtitle(cities[x]) + 
    labs(y = "Weekly MMET", x = "Scenarios") + ylim(0, limit)
  print(y)
